---
title: Disease data report
date: now
execute:
  echo: false
  warning: false
---

```{r}
library(dplyr)
library(DT)

fint <- function(x){
  format(x, big.mark=",")
}
```


```{r}
targets::tar_load(disease_data_files)
targets::tar_load(raw_disease_data)
targets::tar_load(disease_data)
targets::tar_load(imputated_disease_data)
targets::tar_load(valid_disease_data)
```

## Source files

The following original file were considered:

```{r}
list.files(disease_data_files)
```

## Raw data

The raw dataset contains `r fint(nrow(raw_disease_data))` rows and `r fint(length(raw_disease_data))` variables.

Below, the first 100 values of the dataset.

```{r}
head(raw_disease_data, 100) %>% datatable()
```

## Imputated dataset

The raw dataset contains `r fint(nrow(imputated_disease_data))` rows and `r fint(length(imputated_disease_data))` variables.

Below, the first 100 values of the dataset.

```{r}
head(imputated_disease_data, 100) %>% datatable()
```

## Valid dataset

The valid dataset contains `r fint(nrow(valid_disease_data))` rows and `r fint(length(valid_disease_data))` variables.

Below, the first 100 values of the dataset.

```{r}
head(valid_disease_data, 100) %>% datatable()
```

## Aggregated dataset

The aggregated dataset contains `r fint(nrow(disease_data))` rows and `r fint(length(disease_data))` variables.

Below, the first 100 values of the dataset.

```{r}
head(disease_data, 100) %>% datatable()
```


